Comparative vaccine effectiveness of ChAdOx1 versus BNT162b2 in Health and Social Care workers in England: Supplementary materials

### 2021-09-09 analysis/report/draft-manuscript.Rmd
separate same/different second dose types; fix in-line code

  plot_cmlinc <-
    ggplot(cmlinc)+
    geom_step(aes(x=tstop, y=(1-survival)*1000, group=vax1_az_descr, colour=vax1_az_descr))+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=(1-survival.ll)*1000, ymax=(1-survival.ul)*1000, group=vax1_az_descr, fill=vax1_az_descr), alpha=0.1)+
    geom_hline(aes(yintercept=0), colour='black')+
    facet_grid(cols=vars(outcome_descr))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=28),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      limits = c(0L,NA)
    )+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Marginalised\ncumulative incidence\nper 1000",
      colour=NULL
    )+
    theme_minimal()+
    theme(
      legend.position=c(0.05,0.95),
      legend.justification = c(0,1),
      legend.direction = "vertical",
      axis.text.x.top=element_text(hjust=0),

@@

  plot_riskdiff <-
    ggplot(riskdiff)+
    geom_hline(aes(yintercept=0), colour='black')+
    geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
    facet_grid(cols=vars(outcome_descr))+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=28),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    coord_cartesian(ylim= c(-5, 5))+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Difference\nin cumulative incidence\nper 1000",
      colour=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y.left = element_line(colour = "black"),

@@

At 18 weeks post-vaccination, the absolute risk difference for a positive SARS-CoV-2 test was `r filter(riskdiff, outcome=="postest", tstop==7*18)$diff_format` `r filter(riskdiff, outcome=="postest", tstop==7*18)$diff_CI`), for COVID-19 A&E attendances was `r filter(riskdiff, outcome=="covidemergency", tstop==7*18)$diff_format` (`r filter(riskdiff, outcome=="covidemergency", tstop==7*18)$diff_CI`) and for COVID-19 hospital admissions was `r filter(riskdiff, outcome=="covidadmitted", tstop==7*18)$diff_format` `r filter(riskdiff, outcome=="covidadmitted", tstop==7*18)$diff_CI`.

>>>>

  plot_cmlinc <-
    ggplot(cmlinc)+
    geom_step(aes(x=tstop, y=(1-survival)*1000, group=vax1_az_descr, colour=vax1_az_descr))+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=(1-survival.ll)*1000, ymax=(1-survival.ul)*1000, group=vax1_az_descr, fill=vax1_az_descr), alpha=0.1)+
    geom_hline(aes(yintercept=0), colour='black')+
    facet_grid(cols=vars(outcome_descr))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=28),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      limits = c(0L,NA)
    )+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Marginalised\ncumulative incidence\nper 1000",
      colour=NULL
    )+
    theme_minimal()+
    theme(
      legend.position=c(0.95,0.95),
      legend.justification = c(1,1),
      legend.direction = "vertical",
      axis.text.x.top=element_text(hjust=0),

@@

  plot_riskdiff <-
    ggplot(riskdiff)+
    geom_hline(aes(yintercept=0), colour='black')+
    geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
    facet_grid(cols=vars(outcome_descr))+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=28),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    coord_cartesian(ylim= c(-2.5, 2.5))+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Difference\nin cumulative incidence\nper 1000",
      colour=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y.left = element_line(colour = "black"),

@@

At 18 weeks post-vaccination, the absolute risk difference for a positive SARS-CoV-2 test was `r filter(riskdiff, outcome=="postest", tstop==7*18)$diff_format` `r filter(riskdiff, outcome=="postest", tstop==7*18)$diff_CI`, for COVID-19 A&E attendances was `r filter(riskdiff, outcome=="covidemergency", tstop==7*18)$diff_format` `r filter(riskdiff, outcome=="covidemergency", tstop==7*18)$diff_CI` and for COVID-19 hospital admissions was `r filter(riskdiff, outcome=="covidadmitted", tstop==7*18)$diff_format` `r filter(riskdiff, outcome=="covidadmitted", tstop==7*18)$diff_CI`.

### 2021-09-09 analysis/report/draft-supplement.Rmd
separate same/different second dose types; fix in-line code

  outcomes <- 
    c(
      "postest",
      "emergency",
      "covidadmitted"
    ) %>% 
    set_names(., .)

@@

#### Supplmentary Figure 2: Second dose interval by vaccine type

@@

```{r seconddose_postest, echo=FALSE, message=FALSE, warning=FALSE, out.width='90%', fig.height=8, results='asis'}
plot_seconddose_all <- read_rds(here("output", "descriptive", "secondose", "plot_seconddose_all.rds"))
plot_seconddose_all
```

>>>>

  outcomes <- 
    c(
      "postest",
      "covidemergency",
      "covidadmitted"
    ) %>% 
    set_names(., .)

@@

#### Supplmentary Figure 2a: Second dose interval, where second dose vaccine is same as first dose vaccine

@@

```{r seconddose_same, echo=FALSE, message=FALSE, warning=FALSE, out.width='90%', fig.height=8, results='asis'}
read_rds(here("output", "descriptive", "seconddose", "plot_seconddose_samebrand.rds"))
```

#### Supplmentary Figure 2b: Second dose interval, where second dose vaccine is different than the first dose vaccine

```{r seconddose_diff, echo=FALSE, message=FALSE, warning=FALSE, out.width='90%', fig.height=8, results='asis'}
read_rds(here("output", "descriptive", "seconddose", "plot_seconddose_diffbrand.rds"))
```
